|

### 2022-02-28 paper/dcpo_demsupport.Rmd
replication data updated; fixed #42, fixed #40; relate with #36

The three authors contributed equally to this work. 
We thank the editors and anonymous reviewers for their helpful comments.
All errors remain our own.
Replication files are available at the American Political
Science Review Dataverse: https://doi.org/XXXX.

@@

    # wrangling
    here,
    broom,
    tidyverse,
    glue)

@@

source(here("R", "customFunctions.R")) ## analyzing and presenting functions

@@

```{r data-input, include=FALSE}
## Replication data
load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/cws59/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/cgxjd/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
load(here("data", "exp_claassen_input.rda")) # Source???

@@

saveRDS(result_clsAJPS,
        file = here::here("output", "estimates_clsMeanAJPS.RDS"))  
```

@@

load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

saveRDS(mocresult_correctAPSR,
        file = here::here("output", "estimates_moc_correctAPSR.RDS"))
```

@@

saveRDS(mocresult_expAPSR,
        file = here::here("output", "estimates_moc_expcorAPSR.RDS"))
```

@@

```{r dcpodata-input, include=FALSE}
## Replication data
load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xxxx/download
load(here("data", "dcpo_apsr.rda"))  # https://osf.io/xxxx/download
load(here("data", "dcpo_input_update22.rda"))  # https://osf.io/xxxx/download

@@

saveRDS(mocdcpo_APSR,
        file = here::here("output", "estimates_moc_dcpoAPSR.RDS"))
```

@@

Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at https://doi.org/XXXX.

>>>>

The three authors contributed equally to this work. 
We thank the editors and anonymous reviewers for their helpful comments.
All errors remain our own.
Replication files are available at the American Political
Science Review Dataverse: https://doi.org/10.7910/DVN/YM67QE.

@@

    # wrangling
    here,
    broom,
    tidyverse,
    glue,
    janitor,
    purrr,
    tibble,

    # compiling
    rmarkdown,
    bookdown)

@@

source(here("customFunctions.R")) ## analyzing and presenting functions

@@

```{r data-input, include=FALSE}
## Data relocation

if(!dir.exists("data")) {
    dir.create("data")
    file.copy(
        c(
            "correct_cls_ajps.rda",
            "correct_cls_apsr.rda",
            "expcor_cls_ajps.rda",
            "expcor_cls_apsr.rda",
            "exp_claassen_input.rda"
        ),
        "data"
    )
}

if (!dir.exists("output")) {
    dir.create("output")
    file.copy(
        c(
            "estimates_clsMeanAPSR.RDS",
            "estimates_clsMeanAJPS.RDS",
            "estimates_moc_correctAJPS.RDS",
            "estimates_moc_expcorAJPS.RDS",
            "estimates_moc_correctAPSR.RDS",
            "estimates_moc_expcorAPSR.RDS",
            "estimates_moc_dcpoAPSR.RDS",
            "estimates_moc_dcpoAJPS.RDS"
        ),
        "output"
    )
}

## Loading replication data
load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/cws59/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/cgxjd/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
load(here("data", "exp_claassen_input.rda")) # https://osf.io/fcyn3/download

@@

saveRDS(result_clsAJPS,
        file = here("output", "estimates_clsMeanAJPS.RDS"))  
```

@@

load(here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

saveRDS(mocresult_correctAPSR,
        file = here("output", "estimates_moc_correctAPSR.RDS"))
```

@@

saveRDS(mocresult_expAPSR,
        file = here("output", "estimates_moc_expcorAPSR.RDS"))
```

@@

```{r dcpodata-input, include=FALSE}
file.copy(
        c(
            "dcpo_ajps.rda",
            "dcpo_apsr.rda",
            "exp_dcpo_input.rda"
        ),
        "data"
    )

file.copy(
        c(
            "estimates_moc_dcpoAPSR.RDS",
            "estimates_moc_dcpoAJPS.RDS"
        ),
        "output"
    )

## Replication data
load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xw9fr/download
load(here("data", "dcpo_apsr.rda"))  # https://osf.io/j7kn3/download
load(here("data", "exp_dcpo_input.rda"))  # https://osf.io/r2pe8/download

@@

saveRDS(mocdcpo_APSR,
        file = here("output", "estimates_moc_dcpoAPSR.RDS"))
```

@@

Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at https://doi.org/10.7910/DVN/YM67QE.
